Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
Update

To understand \sys better under a realistic workload, we use a large pipeline inspired by the introductory program of Hadoop's Definitive Guide~\cite[Chapter 2]{hadoop:15}.
At a high level,

The original task can be thought of comprising three sub-tasks:
  download weather data from NCDC (shell), convert them to a format that is Hadoop-friendly (shell), and process them to identify the maximum temperature (Hadoop).

---only one of which is the focus of the chapter

It is presented to demonstrate the benefits of Hadoop is well suited to tackle.

The Java program required for this

The effort required to write this pipeline is astonishingly low:
  it amounts to 240 characters 
(Some effort is required to understand NCDC's weather format, but this is true for any program processing this dataset.)

The pipeline starts with a few stages in \sta  that generate URLs;
  these URLs point to index files, each one of which contains pointers 
The stream of index files is analyzed (4 stages) to extract the URLs of the compressed data files.
It is then passed again through a download command
After downloading and uncompressing these files, the stream is analyzed to extract the maximum temperature.

A less obvious lesson from this case was that  
First, large, complex pipelines enable significant freedom in how to express some stages.
Several stages in the original program are compressed into a single \ttt{awk} script;
  unfortunately, \ttt{awk} is too general to have a helpful distributability signature.
For example, the \ttt{sort} command at the end is an expensive version of extracting the maximum element;
  this could have been expressed with a simple \ttt{awk} script that only keeps track of the max.

The Hadoop program 
Hadoop 3.2.1
openjdk 11.0.5
ruby 2.5.5p157

few different ways to write some phases, 
  for example, 
A large pipeline resulted in a couple of 
An interesting lesson here was that there are multiple
First, longer pipelines can be written in multiple ways
It is worth noting
These are

@@

>>>>

To understand \sys better under a realistic workload, we use a large pipeline inspired by the introductory program of Hadoop's Definitive Guide~\cite[Chapter 2]{hadoop:15}.
At a high level, the goal is to process multi-year weather data from NCDC to identify the temperature over the past several years.
The original task, as presented in the book, can be thought of comprising three sub-tasks:
  download weather data from NCDC (shell), convert them to a format that is Hadoop-friendly (shell), and process them to identify the maximum temperature (Hadoop).
Only the last of these tasks is the real focus of the chapter, demonstrate the benefits of using distributed analytics system such as Hadoop.

For \sys, we consider the full pipeline that implements all three sub-tasks---from fetching data to outputting the maximum temperature.
The pipeline starts with a few stages in \sta  that generate URLs;
  these URLs point to index files, each one of which contains pointers to compressed data files.
The stream of index files is then analyzed (4 stages) to extract the URLs of the data files, passed again through the command for downloading data.
After downloading and uncompressing these files, the stream is analyzed to extract the maximum temperature (another 4 stages).

% The first interesting result 
The effort required to write this pipeline is astonishingly low:\footnote{
  Some effort is required to understand NCDC's weather format, but this is true for any program processing this dataset.
}
  it amounts to 14 stages and, when expressed as a single line, only 240 characters.
The Hadoop program, expressed in Java and only capturing the 4 last stages, is about 117 lines of Java code---not accounting for code moving input and output in and out of HDFS.

In terms of execution time, with two Hadoop datanodes running on Hadoop 3.2.1 and Openjdk 11.0.5 without any replication (\ie fault-tolerance), the Hadoop program takes 6m22s for data processing and 1:09 for moving the dataset to HDFS.
For the same amount of parallelism, \sys takes 4m30.554s---but this includes downloading and uncompressing the data files.

@@

A less obvious take-away from this case was that large, complex pipelines enable significant freedom in how to express their stages.
Several stages in the original shell program (taken from the book) are expressed as a single \ttt{awk} script;
  unfortunately, \ttt{awk} is too general to have a meaningful distributability signature.
A much simpler pipeline that builds on built-in \unix primitives is trivially distributable, 
  but might not perform as well in the centralized case.
% For example, the \ttt{sort} command at the end is an expensive version of extracting the maximum element;
%   this could have been expressed with a simple \ttt{awk} script that only keeps track of the max.

% few different ways to write some phases, 
%   for example, 
% A large pipeline resulted in a couple of 
% An interesting lesson here was that there are multiple
% First, longer pipelines can be written in multiple ways
% It is worth noting
% These are
%
